The Place of the Local Group in the Cosmic Web

### 2014-08-12 paper/main.tex
updated plots in the manuscript
new abstract

@@

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  We use the Hessian of the gravitational
potential to classify regions in the cosmic web as a peak, sheet,
filament or void.  The LG is represented by two samples of halos
pairs. The first is a general sample composed by halo pairs with
similar masses and isolation criteria as observed in the LG.  The
second is a subset with additional kinematic constaints. We find that
the pairs in the LG sample with all constraints are: i) Preferentially
located in filaments and sheets, ii) located in in a narrow range of
local overdensity $0<\delta<4$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.5<p<0.5$.  iii) Clearly aligned with the cosmic web,
in particular for pairs in filaments/sheets the orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane. A stronger alignment is present for the vector linking
the two halos, which lies along the filament or the sheet plane.  We
show that the first and second results are expected trends with the LG
total mass. However, the strong alignment with the cosmic web cannot
be explained by a simple mass dependency.

@@

%lg rare
The spatial and kinematic configuration of the Local Group
(LG) galaxies is rare to find in the local Universe and in cosmological
simulations. 
The LG is dominated by the two big spirals MW and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent to a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf}
\caption{Mass distribution of pairs in the different environments
for the general sample.
The shaded regions show the mass ranges of $2\sigma$ and $3\sigma$
samples.  
\label{fig:median_fraction}}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
\caption{Mass dependency of the average dark matter overdensity (left),
  web ellipticity (middle) and web absolute value prolateness (right) at the
  pair location.
\label{fig:median_overdensity}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.46\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb.
    \label{fig:alignment_n}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.46\textwidth]{alignments_e1_r_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e2_r_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e3_r_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb.
    \label{fig:alignment_r}}  
\end{figure}

%\begin{figure}
%  \begin{center}
%    \includegraphics[width=0.48\textwidth]{scheme.pdf}
%    \caption{Schematic picture of the strongest alignment tendencies in
%      the the General and $2\sigma$-$3\sigma$ samples. The alignment
%      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
%      reported in \citet{ForeroRomero2014} for all halos regardles of its
%      mass.
%      \label{fig:scheme}}
%  \end{center}
%\end{figure}

%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf} 
%\caption{Mass dependency of the fraction of pairs in the different
%  environemnts.
%\label{fig:median_fraction}}
%\end{center}
%\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure}

%\begin{figure*}
%\begin{center}
%  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
%\end{center}
%\caption{Ellipticity and prolateness versus the overdensity for the pairs
%in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
%\end{figure*}

%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
%\end{center}
%\caption{Overdensity distribution for the pairs in the three samples.
%    \label{fig:density}}  
%\end{figure}

>>>>

%@arxiver{fig1.pdf,fig4.png,fig15.eps}

@@

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
in the cosmic web as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane. 
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignment with the cosmic web cannot be explained
by a simple mass dependency. 
This precise characterization of the expected place of the LG in the
cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
understanding of diverse features characterizing the Milky Way and the
Andromeda galaxies.

@@

The spatial and kinematic configuration of the Local Group
(LG) galaxies is rare to find in the local Universe and in cosmological
simulations. 
The LG is dominated by the two big spirals MW and M31, the next
most-luminous galaxy is M33 which is $\sim 10$ times less massive than
M31, followed by several less luminous dwarf galaxies, up to a
distance of $\sim 3$\mpc.   
The velocity vector of M31, with a low
tangential velocity is consistent to a head-on collision orbit toward
the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig1.pdf}
\caption{Mass distribution of pairs in the different environments
for the general sample.
The shaded regions show the mass ranges of $2\sigma$ and $3\sigma$
samples.  
\label{fig:median_fraction}}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.31\textwidth]{fig2a.pdf}
  \includegraphics[width=0.32\textwidth]{fig2b.pdf}
  \includegraphics[width=0.32\textwidth]{fig2c.pdf}
\caption{Mass dependency of the average dark matter overdensity (left),
  web ellipticity (middle) and web absolute value prolateness (right) at the
  pair location. 
\label{fig:median_overdensity}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb.
    \label{fig:alignment_n}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.32\textwidth]{fig4a.pdf}
  \includegraphics[width=0.32\textwidth]{fig4b.pdf}
  \includegraphics[width=0.32\textwidth]{fig4c.pdf}
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb.
    \label{fig:alignment_r}}  
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig5.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{fig6.pdf}
\end{center}
\caption{Alignment between the two angular momentum vectors of the two
  halos in the pair.
    \label{fig:jj_alignment}}  
\end{figure}
